---
title: "LANDFIRE-Powered Assessments"
output: 
  flexdashboard::flex_dashboard:
    theme: lumen
    css: styles.css

---


```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(sf)


# Load the shapefile

assessments <- st_read("data/web_reports.shp") %>%
  st_transform(crs = 4326)

```


# Assessments 

## Column {data-width=650}

### 


```{r echo=FALSE, message=FALSE, warning=FALSE}


tol_muted_palette <- colorFactor(c('#88CCEE', '#44AA99', '#117733', '#332288', '#DDCC77', '#999933','#CC6677', '#882255', '#AA4499', '#52504a'), assessments$org_name) # from https://zenodo.org/records/3381072

map <- leaflet() %>%
  addTiles() %>%
  addPolygons(data = assessments, 
              color = ~tol_muted_palette(org_name), 
              weight = 2, 
              opacity = 1, 
              fillOpacity = 0.3) %>%
  setView(lng = -96, lat = 37.8, zoom = 4)

map
```

## Column 2 {data-width=350}

### 

**What do these assessments tell us?**

LANDFIRE-Powered Landscape Assessments allow users to start exploring trends, landscape conversions and natural resource management options. 

Based on current LANDFIRE products, these assessments provide a starting point for future analysis and can help users understand the context of current ecosystems conditions and the role of disturbances within the historical context of these landscapes.

**Getting Started**

- Hover over an assessment to examine
- Click the link to the external dashboard
- Start exploring the individual assessment

Each assessment was created individually and may reflect the specific needs of the assessment partners, as such assessments may vary.  

**Why LANDFIRE?**

LANDFIRE provides complete, landscape-scale products using standardized legends and methodologies. These products are regularly updated and include historical information including [Biophysical Settings Products](https://landfire.gov/vegetation/bps), [Historic Fire Regime](https://landfire.gov/fire-regime) and [Historic Disturbance](https://landfire.gov/disturbance/hdist) Products. 

**Why This Matters?**

Natural resource professionals need versatile, current and continuous data to support their analysis decisions. These assessments are just a sample of what is possible when LANDFIRE products are creatively applied to natural resource questions. All maps, input datasets and further assistance can be obtained by contacting TNC Ecologist, [Randy Swaty](mailto:rswaty@tnc.org). 

**Assessments can help answer landscape questions such as:**

- How have regional fire regimes changed over time? (navigate to assessment of interest, explore on Past tab) 
- What broad vegetation trends are occurring within a landscape? (navigate to assessment of interest, explore on Comparing tab)
- What are the most dominant lifeforms and how does this compare with local knowledge of a specific area? (navigate to assessment of interest, explore on Present tab)



# Input Data and Process 

* add links to data
* add code and/or link to code
* short methods


# Forest Assessments 


# About 

[LANDFIRE](https://landfire.gov/) (Landscape Fire and Resource Management Planning Tools) is a shared program between the U.S. Department of Agriculture Forest Service Fire and Aviation branch and the U.S. Department of the Interior. 

LANDFIRE provides 25+ national landscape-scale geo-spatial products, 950 vegetation models, and a suite of tools that support all-lands planning, management, and operations. Included in the product suite are current and historic conditions including ecosystem dynamic models that can be used for conservation, fire planning, and landscape management decisions.

The Nature Conservancy (TNC) is a Major Partner in the LANDFIRE Program supported by a cooperative agreement through USDA Forest Service. TNC’s LANDFIRE Team works closely with the LANDFIRE Business Leads, program staff, and other partners to provide support to LANDFIRE and the user community by:

- Helping users understand the strengths, weaknesses, and appropriate uses of LANDFIRE products.

- Locating, obtaining, and using geospatial data, tools, and models for fire and natural resource management, planning, and implementation.

- Identifying and comparing management priorities, evaluating threats to ecosystems, and exploring outcomes under alternative management scenarios.


Still have questions? LANDFIRE is here to help.

Ask the [LANDFIRE Helpdesk](mailto:helpdesk@landfire.gov)

Search the [LANDFIRE Helpdesk Dashboard](https://landfire.gov/helpdesk) (see what others are asking and find solutions to common problems)

Search (& subscribe to) the [LANDFIRE YouTube Channel](https://www.youtube.com/@LANDFIREvideo) (see tutorials, Office Hours, quick demonstrations)

