---
title: "LANDFIRE-Powered Assessments"
output: 
  flexdashboard::flex_dashboard:
    theme: journal
    storyboard: true
    css: styles.css

---


```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(sf)


# Load the shapefile

assessments <- st_read("data/web_reports.shp") %>%
  st_transform(crs = 4326)

```


### Assessments {data-commentary-width=500}

```{r echo=FALSE, message=FALSE, warning=FALSE}


tol_muted_palette <- colorFactor(c('#88CCEE', '#44AA99', '#117733', '#332288', '#DDCC77', '#999933','#CC6677', '#882255', '#AA4499', '#52504a'), assessments$org_name) # from https://zenodo.org/records/3381072

map <- leaflet() %>%
  addTiles() %>%
  addPolygons(data = assessments, 
              color = ~tol_muted_palette(org_name), 
              weight = 2, 
              opacity = 1, 
              fillOpacity = 0.3) %>%
  setView(lng = -96, lat = 37.8, zoom = 4)

map
```

*** 

**The what, why, how and who of these assessments**

LANDFIRE-powered landscape assessments are crucial for understanding and managing the condition of ecosystems and disturbance regimes across large landscapes. These assessments provide comprehensive data on vegetation, fuels, and fire regimes, which are essential for effective land management and conservation planning. By leveraging LANDFIRE's nationally consistent geospatial layers, land managers can make informed decisions to mitigate wildfire risks, restore habitats, and maintain ecological balance1.

The LANDFIRE program is a collaborative effort between the U.S. Department of Agriculture (USDA) Forest Service and the U.S. Department of the Interior (DOI). This interagency initiative brings together experts in wildland fire management, ecology, and remote sensing to produce high-quality, standardized data. The program's goal is to support federal, state, and local agencies, as well as non-governmental organizations, in their efforts to manage and protect natural resources effectively1.

To conduct a LANDFIRE-powered landscape assessment, users can access a suite of tools and datasets provided by the program. These include detailed maps, ecological models, and databases that describe landscape change, vegetation, and fire behavior. Users can integrate this data into their geographic information systems (GIS) to analyze current conditions, predict future scenarios, and develop management strategies. The interactive LANDFIRE Map Viewer also allows users to visualize and download data layers, making it easier to apply this information in practical, on-the-ground decision-making

### Input Data and Process 

* add links to data
* add code and/or link to code
* short methods


### Forest Assessments


### About the Team


